Similar Article Detection Using Locality Sensitive Hashing Technique on Wikipedia\titlenote{This effort is part of the CMSC828G, Data Intensive Computing with MapReduce, class project.}

### 2013-04-29 article/sigproc-sp.tex
Started algorithm and implementation sections.

\numberofauthors{5} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor Samet Ayhan\\
       \affaddr{University of Maryland, Department of Computer Science}\\
       \affaddr{College Park, Maryland 20740}\\
       \email{sayhan@cs.umd.edu}
% 2nd. author
\alignauthor Joshua Bradley\\
       \affaddr{University of Maryland, Department of Computer Science}\\
       \affaddr{College Park, Maryland 20740}\\
       \email{jgbradley@cs.umd.edu}
% 3rd. author
\alignauthor Sarah Weissman\\
       \affaddr{University of Maryland, College of Information Studies}\\
       \affaddr{College Park, Maryland 20740}\\
       \email{sweissman@umd.edu}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.

@@

\section{Algorithm Utilizing Locality Sensitive Hashing}
In this section, we introduce the algorithm that utilizes the locality sensitive hashing.

\subsection{Design}
We explain the design here...

\subsection{Implementation}
We explain the implementation here...

@@

\subsection{Optimizations}	 
We explain optimizations here...

\subsubsection{Optimization-1}
An optimization we realized...

>>>>

\numberofauthors{5} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor Samet Ayhan\\
       \affaddr{University of Maryland, Department of Computer Science}\\
       \affaddr{College Park, Maryland 20740}\\
       \email{sayhan@cs.umd.edu}
% 2nd. author
\alignauthor Joshua Bradley\\
       \affaddr{University of Maryland, Department of Computer Science}\\
       \affaddr{College Park, Maryland 20740}\\
       \email{jgbradley@cs.umd.edu}
% 3rd. author
\alignauthor Sarah Weissman\\
       \affaddr{University of Maryland, College of Information Studies}\\
       \affaddr{College Park, Maryland 20740}\\
       \email{sew@umd.edu}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.

@@

\section{Algorithm Utilizing Locality Sensitive Hashing}

In this section, we introduce the algorithm that utilizes the locality sensitive hashing.

In order to measure document similarity we use a common LSH technique known as minhashing \cite{}. A minhash signature on a text document is calculated using a parametrized family of hash functions $F_i$, $1 \le i \le N$. In our case input documents are sentences. Each sentence is broken up into n-gram ``shingles''. For each shingle set $S$ we calculate $\{min_{s \in S}(F_i(s)\}$, the set of minimum hashes over the hash family. The signature on a document d is a vector of $K$ minhashes from the set of minimum hashes. In order to minimize false negatives we apply the technique sometimes known as ``banding'' \cite{Ullman} where multiple signatures are produced for each input document.

\subsection{Design}
Since signature techniques such as LSH are easily parallelized we designed our algorithm around the MapReduce framework.

Describe MapReduce.

Because the minhash technique is parametrized by several values, including shingle length, signature vector size and number of signatures calculated, these values can also be considered as inputs for the MapReduce algorithm.

\begin{table}
MapReduce pseudocode:
\begin{verbatim}
initialize(){
 # configure and set up algorithm parameters
 # F = hash family;
 # L = shingle length;
 # K = vector length;
 # N = number of signatures to emit;
}

map(docid d, wikipage p){
  int sentence ct = 0;
  while s = nextSentence(p){
    shingles = shingleSet(s,L);
    minhashes = new List(|F|);
    for i = 1 ... |F|:
      minhashes[i] = Infinity;
    for g in shingles:
      for i = 1 ... |F|:
        minhashes[i] = min(F_i(g),minhashes[i]);
    for i = 1 ... N:
      sig = select(K, minhahses);
      emit(sig,(docid,sentencect));
    sentencect++;
  }
}
\end{verbatim}

\begin{verbatim}
reduce(signature sig, sentenceids [(d1,s1),(d2,s2) ...]){
  if [[(d1,s1),(d2,s2) ... ]| > 1:
    emit(sig, [(d1,s1), (d2,s2), ...]);
}
\end{verbatim}
\end{table}

\subsection{Implementation Details}

Our implementation is built on top of the Apache Hadoop MapReduce framework, using utilities from the Cloud9 library for parsing Wikipedia page text from the Wikipedia XML dump format. Sentences are parsed out over each document using a regular expression. Sentences that are too large or too small are discarded. The family of hash functions is implemented using a ``Multiply Shift''  \cite{} hashing scheme and is generated from a random seed using the Java Random class. The hash family is also parametrized by hash output key size and this value can be configured to affect the size of the output signatures.

@@

\subsection{Optimization}

We explain optimizations here...

\subsubsection{Parameter Optimization}

As mentioned above the minhash algorithm is parametrized by several values, including shingle length, length of hash vectors, number of hash bands, and hash output size. Each of these parameters has an impact on the error rates in the minhash output.

An optimization we realized...
